During the evaluation of the sample circuits, inaccuracies in the \sdffile\ 
files have been encountered. 
Therefore Python scripts have been created which can create custom \sdffile\ 
files. 
Moreover, the tool can not incorporate INTERCONNECT delays yet, and therefore 
\sdffile\ files containing such delay need to be adapted.

The process consists of two scripts:
\begin{enumerate}
	\item \file{generateDependencies.py}: The \emph{dependency tree} of the 
	circuit has to be extracted. 
	This is done by reading the standard \sdffile\ file, and extracting all 
	INTERCONNECTs. 
	This yields all output to input connections. 
	Based on these results the output to output connections are generated. 
	These results are stored in a dictionary, where for each gate instance the 
	name of the previous output and its own output are stored.
	\item \file{extractSdf.py}: In the second step the result (\vcdfile\ file) 
	of a \spice\ simulation is used to generate the custom \sdffile\ file. 
	The simulation should have sufficient transitions with long pauses during 
	each transition so that for each gate instance and each input the falling 
	and rising time can be extracted from the \vcdfile\ file. 
	If there are more delay values for one value in the \sdffile, the average 
	of these delay values is used.
	
	The final step of the script is that the values in the standard \sdffile\ 
	file are overwritten with the generated values. 
\end{enumerate}

Requirements:
\begin{itemize}
	\item standard \sdffile\ file.
	\item \vcdfile\ file which contains the \spice\ simulation results.
\end{itemize}

Note that the delay for an instance is always calculated from the output of the 
previous instance to the output of this instance. Of course, one could also 
calculate the delay from the input of the current gate to the next gate, but 
then there are multiple possibilities, since the gate could drive several other 
gates.

Note that the scripts are tailored for the sample circuits, and that they need 
to be generalized so that they can be used for all circuits.